Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-20 paper.tex
Add brief mention of SpurSelectiveCompactor.  Now the reference to SpurSelectiveCompactor. in sec 3.3 "Snapshot discussion makes sense.

>>>>

\subsection{Mark-SelectiveCompact}
We added a new algorithm designed to reduce the pause time due to compaction.  This algorithm, to be described fully elsewhere, chooses sparsely populated segments and compacts these to an empty segment to reduce fragmentation.  It relies on Spur's implicit following of forwarding pointers to update references to moved objects without requiring a complete pass over the heap.
